Project

### 2022-03-31 Project/DraftR.Rmd
Update DraftR.Rmd

# Load Package
```{r}

library(tidyr)
library(MASS)
library(MuMIn)
library(ggplot2)
library(reshape2)
library(grid)
library(gridExtra)
library(ggfortify)
library(dplyr)

@@

###NK & HB phenology data
phenNK <- read.csv("./Data/HargreavesEcolLett data phenologyNK.csv")
phenHB <- read.csv("./Data/HargreavesEcolLett data phenologyHB.csv")
```

```{r}
str(phenHB)
```

@@

## PCA
```{r}
# delete rows with NA value
USBwithF1NA <- USBwithF1 %>%
    na.omit
names(USBwithF1NA)
```

>>>>

# Load Package
```{r}
library(ape)
library(tidyr)
library(MASS)
library(MuMIn)
library(ggplot2)
library(reshape2)
library(grid)
library(gridExtra)
library(ggfortify)
library(dplyr)

@@

###NK & HB phenology data
phenNK <- read.csv("./Data/HargreavesEcolLett data phenologyNK.csv")
phenHB <- read.csv("./Data/HargreavesEcolLett data phenologyHB.csv")

###Climate by site data
clim <- read.csv("./Data/HargreavesEcolLett data hobo&ibutton summary by site.csv")
```

## Data Check and Modification
```{r}
sapply(clim, class)
```
```{r}
#d.snowpack.10.11=days with snowpack winter 2010-2011
#wTmin.10.11=minimum temperature winter (C) at plant height 2010-2011
#Dec.FebTav.10.11=mean temperature at plant height from Dec1st 2010 - Feb 28th 2011
#d.grows.11=# days in growing season 2011 (start / end of gorwing season determined by sustained snow or frost)
#GDD.grows.11=# growing degree days (Tbase=10C, Tmax capped at 30C) in growing season of 2011
#GDD.yr.11=# growing degree days in 2011 (ie not truncated to estimated growing season)
#avmaxminTJuly.11=mean July 2011 temperature (C) calculated from daily min and max T: mean(July1stmin + July1stmax + July2ndmin + July2ndmax + ... July31stmi + July31stmax)
#avTJuly.11=mean July 2011 temperature (C) calculated from raw data (ie >2 measurements per day)

#hence, convert the above columns into numeric variables
cols.num <- c("d.snowpack.11.12", "wTmin.11.12", "Dec.FebTav.11.12", "d.grows.12", "GDD.grows.12", "GDD.yr.12", "avmaxminTJuly.12", "avTJuly.12", "GDD.grows.13", "GDD.yr.13", "avmaxminTJuly.13", "avTJuly.13", "d.snowpack.13.14", "wTmin.13.14", "Dec.FebTav.13.14")
clim[cols.num] <- sapply(clim[cols.num],as.numeric)
sapply(clim, class)
head(clim)
```
```{r}
#use 'melt' to convert the 'clim' data.frame into long format in which 'transect' and 'site' are identifier variables, while the other are considered as the measured variables.
clim.sea <- melt(clim, id.vars = c('transect','site'), measure.vars = 3:29)
head(clim.sea)
```

@@

## PCA
Take phenology data and look at low v mid v high (Q2 and Q3) 
Are low similar to each other, are mid similar, are high similar 
Origin vs transplant location 
Phenotypic plasticity 
```{r}
# delete rows with NA value??
PhenoNA <- phenmerged %>%
    na.omit
```

```{r}
names(phenmerged)
```
```{r}
str(phenmerged)
```
```{r}
phenmerged$year <- as.factor(phenmerged$year)
row.names(phenmerged) <- phenmerged$X
```
